---
title: "Regression Analyses"
author: "Tim Lai"
date: "3/30/2020"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Loading the data
We load the testing data which includes the regression analyses from both models. 
```{r}
logs <- read.delim("seq_pred.tsv")
dnn <- read.delim("pred.tsv")
```

## Overview of data
The models were trained with a log transform on the scores. We apply a log transform on the scores column to reproduce this. In addition, if we wish to compare the original scores, we need to invert the log on the prediction columns. 
```{r}
logs$logscore <- log(logs$score)
dnn$logscore <- log(dnn$score)

logs$pred <- exp(logs$Lin_Pred)
dnn$pred <- exp(dnn$DNN_Pred)
```
To plot the distribution, we opt for a histogram. We make the bins for the log scores.
```{r}
logs$logscore.binned <- cut(logs$logscore, c(-0.1, 0.6, 1, 3, 6))
logs$logbins <- cut(logs$pred, c(0, 0.6, 1, 3, 6))
dnn$logbins <- cut(dnn$pred, c(0, 0.6, 1, 3, 6))
table(logs$logbins)
table(dnn$logbins)
```

## Including Plots

We first consider the histogram for the original log scores. 
```{r, echo=FALSE}
ggplot(logs) + geom_bar(aes(x=logscore.binned))
```

Finally, we provide the plots for the log predictions with the bins from the model predictions.

```{r, echo=FALSE}
ggplot(logs) + geom_bar(aes(x=logbins))
ggplot(dnn) + geom_bar(aes(x=logbins))
```
